---
title: "Open Stats Lab Additional Analytic Skills in R Using Data from Gino, Kouchaki, and Galinsky (2015)"
author: "Cory J. Cascalheira"
date: "December 10, 2018"
output:
  html_document:
    toc: true
    toc_float: true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
knitr::opts_knit$set(root.dir = "~/GitHub/osl-gino-kouchaki-galinsky-2015/src")
```

# Open Stats Lab
___
Kevin P. McIntyre developed this amazing resource for students of psychology. Check out [Open Stats Lab](https://sites.trinity.edu/osl/) for a collection of all activities.

Each activity includes an article from *Psychological Science*, a data set, and an activity to complete in SPSS. However, if you are an open source fanatic, you could also complete the activity in [JASP](https://jasp-stats.org/). For tips on how to use JASP, check out [this resource](https://osf.io/t56kg/) created by Buchanan, Hopke, and Donaldson (2018).

I prefer to get my hands deep into the data. Dr. McIntyre does not *yet* offer an R activity to accompany the work of [Gino, Kouchaki, and Galinsky (2015)](https://journals.sagepub.com/stoken/default+domain/6XgDSfr6ZHSDs47tx5bu/full), so here is one possible solution written in R.

# Analysis
___
I will perform assumption checks for each test prior to running it. We already know that the data meet all assumptions, otherwise the authors would have used a different analytic approach. However, checking the assumptions is helpful because:

1. reproducibility and accuracy can be verified; and
2. if you are a student, then you should form the habit of testing assumptions.

This analysis will follow the data science workflow advocated by [Garrett Grolemund and Hadley Wickham](https://r4ds.had.co.nz/introduction.html). First, we will set-up our session and import the data. Then, we must clean the data. Next, we will transform, model, and visualize the data to understand it. Finally, we will communicate our findings.

## Import
___
We start by loading the necessary packages.

```{r message=FALSE}
library(tidyverse) # utility & visualization
library(psych) # Cronbach's alpha
library(knitr) # create tables
library(kableExtra) # style tables
library(broom) # calculate effect size
library(car) # Levene's test
library(gmodels) # crosstabs method for chi-square
```

Now we can import the data set. Note the relative path since the working directory has been set.

```{r message=FALSE}
gino <- read_csv("../data/Gino Kouchaki Galinsky 2015 Experiment 3.csv")
```

We can also set the default theme for the exploratory plots we will create as we test the assumptions of the univariate ANOVAs.

```{r}
theme_set(theme_minimal())
```

## Clean
___
Unlike some data sets in the Open Stats Lab series, Dr. McIntyre chose to leave all observations in this file. That is, the data set has 291 observations instead of 288. 

```{r}
glimpse(gino)
```

It appears that we must filter for those participants who passed the manipulation check, `FAILED_MC`, excluding those who failed it. Once we do that, this variable is useless and we can drop it, along with `instr`, `filter`, `MCheck`, the demographic variables and the dummy variables. Keep only one of the two condition variables.

```{r}
gino_clean <- gino %>%
  filter(FAILED_MC == 0) %>%
  select(-c(instr, filter, CONDITION, FAILED_MC, MCheck, age, male),
         -ends_with("Dummy")) %>%
  rename(condition = condition_string)
```

A transformation of condition into a factor is necessary for the one-way ANOVAs.

```{r}
gino_clean <- within(gino_clean, {
  condition <- factor(condition)
})
```

## Understand
___
Our first task is to compute aggregate dependent measures. A chain of pipes makes this task is relatively simple in R. For each dependent measure, we will mutate a new variable that selects individual columns to compute the mean for each row. The aggregate is more useful for future analyses, so the individual measures of impurity, dissonance, and so on will be dropped.

Always save your results as new R data frames to track changes.

```{r}
(gino_means <- gino_clean %>%
  mutate(
    feelings_of_impurity = select(gino_clean, starts_with("impurity")) %>% rowMeans(),
    feelings_of_discomfort = select(gino_clean, starts_with("dissonance")) %>% rowMeans(),
    negative_affect = select(gino_clean, starts_with("neg")) %>% rowMeans(),
    positive_affect = select(gino_clean, starts_with("pos")) %>% rowMeans(),
    embarrassment = select(gino_clean, embarrassed, ashamed) %>% rowMeans(),
    self_alienation = select(gino_clean, starts_with("alien")) %>% rowMeans()
  ) %>%
  select(condition, feelings_of_impurity, feelings_of_discomfort, negative_affect,
         positive_affect, embarrassment, self_alienation, decided_to_help))
```

### Cronbach's Alpha

Cronbach's alpha is a measure of internal consistency ranging from 0 to 1. [Acceptable values](https://www.ncbi.nlm.nih.gov/pmc/articles/PMC4205511/) for the coefficient range from 0.70 to 0.95, although it has been noted that values greater than 0.90 may indicate redundancy. Longer measurement instruments increase internal consistency, but may cause redundancy.

A function exists to calculate Cronbach's alpha in `psych::alpha`. The function takes a data frame of scale items as its primary argument. Select the individual scale items prior to aggregation to compute alpha for each underlying construct.

```{r warning=FALSE}
# Cronbach's alpha for feelings of impurity
gino_clean %>%
  select(starts_with("impurity")) %>%
  psych::alpha()

# Cronbach's alpha for feelings of discomfort
gino_clean %>%
  select(starts_with("dissonance")) %>%
  psych::alpha()

# Cronbach's alpha for negative affect
gino_clean %>%
  select(starts_with("neg")) %>%
  psych::alpha()

# Cronbach's alpha for positive affect
gino_clean %>%
  select(starts_with("pos")) %>%
  psych::alpha()

# Cronbach's alpha for embarrassment
gino_clean %>%
  select(embarrassed, ashamed) %>%
  psych::alpha()

# Cronbach's alpha for self-alienation
gino_clean %>%
  select(starts_with("alien")) %>%
  psych::alpha()
```

After writing their essays, participants answered a questionnaire composed of items on a 7-point scale. The items assessed feelings of impurity ($\alpha = .94$), discomfort ($\alpha = .94$), negative ($\alpha = .93$) and positive ($\alpha = .95$) affect, embarrassment ($\alpha = .90$), and self-alienation ($\alpha = .90$).

### Descriptive Statistics

One method for calculating descriptive statistics uses a pipeline chaining `group_by()` and `summarize()`. First, we need to transform the data into long format using `gather()`. 

Although the activity does not require it, you will notice the upper and lower bounds of the 95% confidence interval in the output. Note that the confidence intervals differ slightly from those reported by Gino, Kouchaki, and Galinsky (2015), which is to be expected. Had we chosen to perform bootstrapping with a call to `quantile()`, the computed 95% confidence intervals would have likely been different from those yielded below. Slight variation of confidence intervals is acceptable.

```{r}
(gino_summary <- gino_means %>%
  select(-decided_to_help) %>%
  gather(key = item, value = score, -condition) %>%
  group_by(condition, item) %>%
  summarize(
    mean = mean(score),
    sd = sd(score),
    n = n(),
    t_star = qt(p = 0.975, df = n - 1),
    upper = mean + (t_star * (sd/sqrt(n))), 
    lower = mean - (t_star * (sd/sqrt(n)))
  ))
```

### APA Style Table

If `item` becames a factor, we can rearrange the order and apply labels that match the publication.

```{r}
(gino_summary <- within(gino_summary, {
  item <- factor(item, 
                 levels = c("self_alienation", "feelings_of_impurity", "feelings_of_discomfort",
                            "negative_affect", "positive_affect", "embarrassment"),
                 labels = c("Self-alienation", "Feelings of impurity", "Discomfort",
                            "Negative affect", "Positive affect", "Embarrassment"))
})) 
```

Isolate the mean and standard deviation, renaming the columns to match APA format.

```{r}
# Drop confidence interval information
(gino_summary_short <- gino_summary %>%
    select(condition, item, mean, sd))

# Rename columns
(gino_summary_short <- gino_summary_short %>%
    rename(
      Variable = item,
      M = mean,
      SD = sd
    ) %>%
    arrange(Variable))
```

The table is too long. Divide this data frame into three R objects, then merge the columns to one master data frame.

```{r}
# Separate by condition
(gino_table <- gino_summary_short %>%
  filter(condition == "inauthenticity") %>%
  ungroup() %>%
  select(Variable, M, SD))

failure <- gino_summary_short %>%
  filter(condition == "failure") %>%
  ungroup() %>%
  select(M, SD)

condition <- gino_summary_short %>%
  filter(condition == "neutral") %>%
  ungroup() %>%
  select(M, SD)

# Prepare table format
(clean_table <- bind_cols(gino_table, failure, condition))
```

The following code is a `kable` in LaTeX form. It saves the table in APA style as a `.png` and displays the output.

```{r}
kable(clean_table, "latex", booktabs = TRUE, digits = 2, align = "lcccccc",
      col.names = c("Variable", "M", "SD", "M", "SD", "M", "SD")) %>%
  add_header_above(header = c(" ", "Inauthenticity" = 2, "Failure" = 2, "Control" = 2)) %>%
  kable_as_image(filename = "../data/results/apa_table")
```

### One-way ANOVA

Now we can conduct a one-way between-groups ANOVA for each construct. The assumptions for this parametic test can be thought of as either met before the study was conducted or tested after data collection.

**Design Assumptions**
1. **Continuous dependent variable** at the interval or ratio level. 

2. **Categorical independent variable** as a factor with three or more levels.

3. **Independence of observations** such that participants are randomly assigned to levels of the factor (i.e., groups) with no overlap.

**Tested Assumptions**
4. **No significant outliers**, which can skew the distribution and affect normality; assessed via boxplots.

5. **Normal distribution** of dependent measures for each group; assessed with Shapiro-Wilk and Q-Q plots.
    - Univariate ANOVAs can tolerate non-normal data.
    - Shapiro-Wilk test is conducted on the residuals of the ANOVA models.
    - The data points in the Q-Q plot should be aligned with the dotted diagonal line if the distribution of the dependent measure is to be considered normal.

6. **Homogeneity of variances** between all groups for each dependent measure; assessed with [Levene's test](https://files.eric.ed.gov/fulltext/EJ809430.pdf) and plot of residuals versus fitted values.
    - Violation of this assumption is most problematic when sample sizes are not *roughly* [equal](https://stats.stackexchange.com/questions/303905/what-affects-levenes-test-sig-value).
    - Homogeneity of variances can be assumed if the red line in [residuals vs. fitted values plot](http://www.sthda.com/english/wiki/one-way-anova-test-in-r) is horizontal.

After each omnibus test, we will conduct pairwise comparisons with a Bonferroni correction to determine which pairs of groups are significantly different. The [Bonferroni correction](https://www.r-bloggers.com/r-tutorial-series-anova-pairwise-comparison-methods/) divides the Type I error rate by the number of levels of the factor (in this case, 3), making the Bonferroni correction a more conservative estimate of significance.

Reporting the direction of comparisons relies on the descriptive statistics calculated above.

The effect size of a one-way ANOVA is partial eta-squared, which we can calculate manually:

$$\eta_p^2 = \frac{SS_\text{condition}}{SS_\text{condition} + SS_\text{residuals}}$$

After creating an `aov` object, we will extract coefficient-level information with `broom::tidy` to code the sum of squares. This prevents transcription error and supports reproducibility.

#### Self-alienation {.tabset .tabset-pills}

```{r}
# Self-alienation
alienation_aov <- aov(self_alienation ~ condition, data = gino_means)

# Partial eta-squared
(alienation_tidied <- tidy(alienation_aov))
alienation_tidied$sumsq[1] / (alienation_tidied$sumsq[1] + alienation_tidied$sumsq[2])

# Pairwise comparisons
pairwise.t.test(gino_means$self_alienation, gino_means$condition,
                p.adjust.method = "bonferroni")
```

A one-way ANOVA using the self-alienation manipulation check as the dependent measure evinced a main effect of condition, *F*(2, 285) = 43.23, *p* < .001, $\eta_p^2 = .23$. Pairwise t-tests corrected by Bonferroni adjustment revealed that participants in the inauthentic condition (*M* = 3.83, *SD* = 1.51) felt a greater distance from the self than participants in either the failure (*M* = 3.21, *SD* = 1.62, *p* = .012) or the control condition (*M* = 1.92, *SD* = 1.19, *p* < .001). Participants reported greater self-alienation when they recalled a failure than when they recalled a recent situation (*p* < .001).

##### Outliers?
```{r}
ggplot(gino_means, aes(x = condition, y = self_alienation)) +
  geom_boxplot()
```

Outliers are present int he neutral condition.

##### Normality?
```{r}
alienation_residuals <- residuals(alienation_aov)
shapiro.test(alienation_residuals)
plot(alienation_aov, 2)
```

Since *p* < .001, we reject the null hypothesis: the data are not normally distributed.

##### Homoscedasticity?
```{r}
leveneTest(self_alienation ~ condition, data = gino_means)
plot(alienation_aov, 1)
```

Since *p* < .001. we reject the null hypothesis: the variances are heterogeneous.

#### Feelings of Impurity {.tabset .tabset-pills}

```{r}
# Feelings of Impurity
impurity_aov <- aov(feelings_of_impurity ~ condition, data = gino_means)

# Partial eta-squared
(impurity_tidied <- tidy(impurity_aov))
impurity_tidied$sumsq[1] / (impurity_tidied$sumsq[1] + impurity_tidied$sumsq[2])

# Pairwise comparisons
pairwise.t.test(gino_means$feelings_of_impurity, gino_means$condition,
                p.adjust.method = "bonferroni")
```

A one-way ANOVA using the composite score of impurity as the dependent measure also revealed a main effect of condition, *F*(2, 285) = 72.29, *p* < .001, $\eta_p^2 = .34$. Pairwise comparisons (with Bonferroni adjustment) revealed significant difference across conditions. Participants who wrote essays about an inauthentic experience (*M* = 3.66, *SD* = 1.82) reported feeling more impure than those who wrote about a failure (*M* = 2.09, *SD* = 1.56, *p* < .001) or recent memory (*M* = 1.21, *SD* = 0.61, *p* < .001). Reported feelings of impurity were higher among participants in the failure than in the control condition (*p* < .001).

##### Outliers?
```{r}
ggplot(gino_means, aes(x = condition, y = feelings_of_impurity)) +
  geom_boxplot()
```

Outliers are present.

##### Normality?
```{r}
impurity_residuals <- residuals(impurity_aov)
shapiro.test(impurity_residuals)
plot(impurity_aov, 2)
```

The data are not normally distributed.

##### Homoscedasticity?
```{r}
leveneTest(feelings_of_impurity ~ condition, data = gino_means)
plot(impurity_aov, 1)
```

Since *p* < .001, we reject the null hypothesis that the variances are homogeneous.

#### Discomfort {.tabset .tabset-pills}

```{r}
# Discomfort
discomfort_aov <- aov(feelings_of_discomfort ~ condition, data = gino_means)

# Partial eta-squared
(discomfort_tidied <- tidy(discomfort_aov))
discomfort_tidied$sumsq[1] / (discomfort_tidied$sumsq[1] + discomfort_tidied$sumsq[2])

# Pairwise comparisons
pairwise.t.test(gino_means$feelings_of_discomfort, gino_means$condition,
                p.adjust.method = "bonferroni")
```

Feelings of discomfort varied across conditions, *F*(2, 285) = 82.67, *p* < .001, $\eta_p^2 = .37$. Pairwise comparisons (with Bonferroni adjustment) revealed that participants who wrote about inauthenticity (*M* = 5.11, *SD* = 1.53) felt the same amount of psychological discomfort as those who wrote about failure (*M* = 4.90, *SD* = 1.64, *p* = 1.00), but reported higher levels than those who wrote about a recent situation (*M* = 2.41, *SD* = 1.71, *p* < .001). Participants reported more discomfort when recalling a memory involving failure than a neutral memory (*p* < .001).  

##### Outliers?
```{r}
ggplot(gino_means, aes(x = condition, y = feelings_of_discomfort)) +
  geom_boxplot()
```

Outliers are present in the inauthenticity condition.

##### Normality?
```{r}
discomfort_residuals <- residuals(discomfort_aov)
shapiro.test(discomfort_residuals)
plot(discomfort_aov, 2)
```

The data are not normally distributed (*p* < .001).

##### Homoscedasticity?
```{r}
leveneTest(feelings_of_discomfort ~ condition, data = gino_means)
plot(discomfort_aov, 1)
```

Since *p* = .312, we fail the reject the null hypothesis; the variances are homogeneous.

#### Negative Affect {.tabset .tabset-pills}

```{r}
# Negative Affect
negative_aov <- aov(negative_affect ~ condition, data = gino_means)

# Partial eta-squared
(negative_tidied <- tidy(negative_aov))
negative_tidied$sumsq[1] / (negative_tidied$sumsq[1] + negative_tidied$sumsq[2])

# Pairwise comparisons
pairwise.t.test(gino_means$negative_affect, gino_means$condition,
                p.adjust.method = "bonferroni")
```

A main effect of condition was found for reported negative affect, *F*(2, 285) = 98.28, *p* < .001, $\eta_p^2 = .41$. Pairwise t-tests with Bonferroni corrections revealed no difference in reported negative affect among participants in the inauthenticity (*M* = 4.63, *SD* = 1.68) and failure (*M* = 4.61, *SD* = 1.73, *p* = 1.00) conditions. Participants who wrote about a recent memory (*M* = 1.88, *SD* = 1.30) were less likely to report negative affect than those who either wrote about inauthenticity (*p* < .001) or failure (*p* < .001). 

##### Outliers?
```{r}
ggplot(gino_means, aes(x = condition, y = negative_affect)) +
  geom_boxplot()
```

Three outliers in the control condition.

##### Normality?
```{r}
negative_residuals <- residuals(negative_aov)
shapiro.test(negative_residuals)
plot(negative_aov, 2)
```

The distribution of reported negative affect violates the assumption of normality.

##### Homoscedasticity?
```{r}
leveneTest(negative_affect ~ condition, data = gino_means)
plot(negative_aov, 1)
```


#### Positive Affect {.tabset .tabset-pills}

```{r}
# Positive Affect
positive_aov <- aov(positive_affect ~ condition, data = gino_means)

# Partial eta-squared
(positive_tidied <- tidy(positive_aov))
positive_tidied$sumsq[1] / (positive_tidied$sumsq[1] + positive_tidied$sumsq[2])

# Pairwise comparisons
pairwise.t.test(gino_means$positive_affect, gino_means$condition,
                p.adjust.method = "bonferroni")
```

Positive affect varied across conditions as well, *F*(2, 285) = 116.76, *p* < .001, $\eta_p^2 = .45$. Pairwise comparisons (with Bonferroni adjustment) revealed that participants who wrote about an inexperience in which they felt inauthentic (*M* = 1.99, *SD* = 1.11) were less likely to report positive affect than those in the control condition (*M* = 4.46, *SD* = 1.77, *p* < .001). Compared to participants who wrote about failure (*M* = 1.84, *SD* = 1.01), those assigned to the control group reported greater positive affect (*p* < .001). Positive affect was the same for participants in both the inauthenticity and failure conditions (*p* = 1.00).

##### Outliers?
```{r}
ggplot(gino_means, aes(x = condition, y = positive_affect)) +
  geom_boxplot()
```

Outliers are present.

##### Normality?
```{r}
positive_residuals <- residuals(positive_aov)
shapiro.test(positive_residuals)
plot(positive_aov, 2)
```

The distribution of reported positive affect is non-normal. 

##### Homoscedasticity?
```{r}
leveneTest(positive_affect ~ condition, data = gino_means)
plot(positive_aov, 1)
```

Since *p* < .001, we reject the null hypothesis; the data are heteroscedastic.

#### Embarrassment {.tabset .tabset-pills}

```{r}
# Embarrassment
embarrassment_aov <- aov(embarrassment ~ condition, data = gino_means)

# Partial eta-squared
(embarrassment_tidied <- tidy(embarrassment_aov))
embarrassment_tidied$sumsq[1] / (embarrassment_tidied$sumsq[1] + embarrassment_tidied$sumsq[2])

# Pairwise comparisons
pairwise.t.test(gino_means$embarrassment, gino_means$condition, 
                p.adjust.method = "bonferroni")
```

Feelings of embarrassment also varied across conditions, *F*(2, 285) = 80.77, *p* < .001, $\eta_p^2 = .36$. Pairwise comparisons (with Bonferroni adjustment) indicated no difference in reported embarrassment between those who wrote an essay about an inauthentic experience (*M* = 4.40, *SD* = 1.71) and those who wrote about failure (*M* = 4.69, *SD* = 1.82, *p* = .71). Participants were less likely to feel embarrassed when writing about a recent situation (*M* = 1.96, *SD* = 1.38) than in a memory involving inauthenticity (*p* < .001) or failure (*p* < .001). 

##### Outliers?
```{r}
ggplot(gino_means, aes(x = condition, y = embarrassment)) +
  geom_boxplot()
```

Outliers are present.

##### Normality?
```{r}
embarrassment_residuals <- residuals(embarrassment_aov)
shapiro.test(embarrassment_residuals)
plot(embarrassment_aov, 2)
```

Since *p* < .001, we reject the null hypothesis; the data violate the assumption of normality.

##### Homoscedasticity?
```{r}
leveneTest(embarrassment ~ condition, data = gino_means)
plot(embarrassment_aov, 1)
```

Since *p* = .016, we reject the null hypothesis; the variances are heterogeneous.

### Chi-square Test

A chi-square test of independence is used to examine whether two categorical variables are associated. It can be conducted in R using `chisq.test()` on a contingency table, or calling that function on two vectors. 

$$H_0: \text{the two variables are independent} \\ H_1: \text{the two variables are associated}$$

Cramer's V is a [measure of association](https://www.r-bloggers.com/example-8-39-calculating-cramers-v/) for categorical variables and be thought of as the effect size of the chi-square test. It is given by the equation:

$$\phi_c = \sqrt{\frac{\chi^2}{N(k - 1)}}$$

This function can be used to calculate Cramer's V:

```{r}
cv.test = function(x,y) {
  CV = sqrt(chisq.test(x, y, correct=FALSE)$statistic /
              (length(x) * (min(length(unique(x)),length(unique(y))) - 1)))
  print.noquote("Cramér V / Phi:")
  return(as.numeric(CV))
}
```

Is the percentage of participants helping the same across groups?

```{r}
# Select helping variable
gino_help <- gino_clean %>%
  select(condition, decided_to_help)

# Conduct chi-square test on contingency table
chisq.test(table(gino_help))

# Cramer's V for all conditions
cv.test(gino_means$condition, gino_means$decided_to_help)
```

The proportion of participants who decided to help varied across conditions, $\chi^2(2, N = 288) = 10.35$, *p* = .006, Cramer's *V* = .19. 

Now we calculate the proportion of those who helped by condition.

```{r}
gino_help %>%
  group_by(condition) %>%
  summarize(
    percentage = mean(decided_to_help)
  )
```

Notice that when we compute chi-square tests on 2 x 2 frequency tables, it may be avisable to use Yate's correction.

```{r}
# Chi-square of inauthenticity vs. failure
gino_help_fail <- gino_help %>%
  filter(condition != "neutral")

# Drop unused factor level
gino_help_fail$condition <- droplevels(gino_help_fail$condition)

chisq.test(table(gino_help_fail))

# Chi-square of inauthenticity vs. neutral
gino_help_neutral <- gino_help %>%
  filter(condition != "failure")

# Drop unused factor level
gino_help_neutral$condition <- droplevels(gino_help_neutral$condition)

chisq.test(table(gino_help_neutral))
```

Here, these values do not match those reported by Gino, Kouchaki, and Galinsky (2015). Let us verify our calculations with an alternative method using a function similar to [CROSSTABS in SPSS](https://www.statmethods.net/stats/frequencies.html).

```{r}
# Crosstabs method: inauthenticity vs. failure
CrossTable(gino_help_fail$condition, gino_help_fail$decided_to_help, 
           format = "SPSS", chisq = TRUE)

# Crosstabs method: inauthenticity vs. neutral
CrossTable(gino_help_neutral$condition, gino_help_neutral$decided_to_help, 
           format = "SPSS", chisq = TRUE)
```

Participants who wrote an essay about an inauthentic memory were likely to help (33.7%) than those who wrote about failure (17.5%, $\chi^2(1, N = 189) = 5.69$, *p* = .017) or a recent situation (16.2%, $\chi^2(1, N = 191) = 6.99$, *p* = .008).

## Communicate
___
After writing their essays, participants answered a questionnaire composed of items on a 7-point scale. The items assessed feelings of impurity ($\alpha = .94$), discomfort ($\alpha = .94$), negative ($\alpha = .93$) and positive ($\alpha = .95$) affect, embarrassment ($\alpha = .90$), and self-alienation ($\alpha = .90$).

**Self-alienation**. A one-way ANOVA using the self-alienation manipulation check as the dependent measure evinced a main effect of condition, *F*(2, 285) = 43.23, *p* < .001, $\eta_p^2 = .23$. Pairwise t-tests corrected by Bonferroni adjustment revealed that participants in the inauthentic condition (*M* = 3.83, *SD* = 1.51) felt a greater distance from the self than participants in either the failure (*M* = 3.21, *SD* = 1.62, *p* = .012) or the control condition (*M* = 1.92, *SD* = 1.19, *p* < .001). Participants reported greater self-alienation when they recalled a failure than when they recalled a recent situation (*p* < .001).

**Feelings of impurity**. A one-way ANOVA using the composite score of impurity as the dependent measure also revealed a main effect of condition, *F*(2, 285) = 72.29, *p* < .001, $\eta_p^2 = .34$. Pairwise comparisons (with Bonferroni adjustment) revealed significant difference across conditions. Participants who wrote essays about an inauthentic experience (*M* = 3.66, *SD* = 1.82) reported feeling more impure than those who wrote about a failure (*M* = 2.09, *SD* = 1.56, *p* < .001) or recent memory (*M* = 1.21, *SD* = 0.61, *p* < .001). Reported feelings of impurity were higher among participants in the failure than in the control condition (*p* < .001).

**Discomfort**. Feelings of discomfort varied across conditions, *F*(2, 285) = 82.67, *p* < .001, $\eta_p^2 = .37$. Pairwise comparisons (with Bonferroni adjustment) revealed that participants who wrote about inauthenticity (*M* = 5.11, *SD* = 1.53) felt the same amount of psychological discomfort as those who wrote about failure (*M* = 4.90, *SD* = 1.64, *p* = 1.00), but reported higher levels than those who wrote about a recent situation (*M* = 2.41, *SD* = 1.71, *p* < .001). Participants reported more discomfort when recalling a memory involving failure than a neutral memory (*p* < .001).

**Negative affect**. A main effect of condition was found for reported negative affect, *F*(2, 285) = 98.28, *p* < .001, $\eta_p^2 = .41$. Pairwise t-tests with Bonferroni corrections revealed no difference in reported negative affect among participants in the inauthenticity (*M* = 4.63, *SD* = 1.68) and failure (*M* = 4.61, *SD* = 1.73, *p* = 1.00) conditions. Participants who wrote about a recent memory (*M* = 1.88, *SD* = 1.30) were less likely to report negative affect than those who either wrote about inauthenticity (*p* < .001) or failure (*p* < .001).

**Positive affect**. Positive affect varied across conditions as well, *F*(2, 285) = 116.76, *p* < .001, $\eta_p^2 = .45$. Pairwise comparisons (with Bonferroni adjustment) revealed that participants who wrote about an inexperience in which they felt inauthentic (*M* = 1.99, *SD* = 1.11) were less likely to report positive affect than those in the control condition (*M* = 4.46, *SD* = 1.77, *p* < .001). Compared to participants who wrote about failure (*M* = 1.84, *SD* = 1.01), those assigned to the control group reported greater positive affect (*p* < .001). Positive affect was the same for participants in both the inauthenticity and failure conditions (*p* = 1.00).

**Embarrassment**. Feelings of embarrassment also varied across conditions, *F*(2, 285) = 80.77, *p* < .001, $\eta_p^2 = .36$. Pairwise comparisons (with Bonferroni adjustment) indicated no difference in reported embarrassment between those who wrote an essay about an inauthentic experience (*M* = 4.40, *SD* = 1.71) and those who wrote about failure (*M* = 4.69, *SD* = 1.82, *p* = .71). Participants were less likely to feel embarrassed when writing about a recent situation (*M* = 1.96, *SD* = 1.38) than in a memory involving inauthenticity (*p* < .001) or failure (*p* < .001).

**Decided to help**. The proportion of participants who decided to help varied across conditions, $\chi^2(2, N = 288) = 10.35$, *p* = .006, Cramer's *V* = .19. Participants who wrote an essay about an inauthentic memory were likely to help (33.7%) than those who wrote about failure (17.5%, $\chi^2(1, N = 189) = 5.69$, *p* = .017) or a recent situation (16.2%, $\chi^2(1, N = 191) = 6.99$, *p* = .008).

# Acknowledgements
___
I am thankful for my advisor, Dr. Brandt A. Smith for introducing me to R, JASP, and OSL. The discipline of psychology is advocating for preregistered, open materials. His encouragement to utilize open data and open source software has positioned me in the middle of the reproducible movement.

I would still be clicking checkboxes and dropdowns to analyze data if it were not for [DataCamp](https://www.datacamp.com), [Alboukadel Kassambara](http://www.sthda.com/english/wiki/r-software), [Jonathan Baron](https://www.sas.upenn.edu/~baron/from_cattell/rpsych/rpsych.html#htoc60), and the team behind [personality-project](http://personality-project.org/r/r.guide.html#withinone).

## Dependencies
This activity was completed using RStudio.

```{r}
devtools::session_info()
```